|

### 2019-12-18 PaperDraft.Rmd
Centered title

---
title: "Tennis"
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "Decemeber 19, 2019"
output: pdf_document
header - input: 
  - \usepackage{float}
bibliography: bibliography.bib

>>>>

---
title: |
  | \vspace{3.5in} \LARGE Predicting the Outcomes of Tennis Tournaments
subtitle: "A Monte Carlo Approach"
author: "Olivia Beck, Emma Lewis, Ryan Volkert"
date: "Decemeber 19, 2019"
output: pdf_document
header - input: 
  - \usepackage{float}
bibliography: bibliography.bib
